Einstein's gravity from a polynomial affine model

### 2016-05-09 AffGR-PRD.tex
Just before the final read-proof

Finally, we analyzed the second order perturbation of the action in Eq.~\eqref{4dfull}, around a maximally symmetric spacetime.

{\huge{\textcolor{red}{Working Here!}}}

>>>>

Finally, we analyzed the second order perturbation of the action in Eq.~\eqref{4dfull}, around a maximally symmetric spacetime. From this analysis it is possible to conclude that, at perturbative level, the number of degrees of freedom are eighteen. These degrees of freedom come from a pair of transverse, symmetric, rank-two-tensors, and a pair of transverse vectors. Moreover, we applied the Lagrangian equivalent of Dirac's formalism for constrained systems (see Ref.~\cite{Diaz:2014yua}), and obtain the same number of physical states---which in principle do not need to coincide, because the perturbative analysis is not exact~\footnote{We want to thank to M.~Blagojevi\'c and B.~Cvetkovi\'c for clarifications in this respect.}.
